### 2021-04-08 submission/manuscript.Rmd
Add R-sq values to fig 4 legend and update readme with here package

library(tidyverse)
library(knitr)

@@

fig_4_pval = 1
fig_4_rsq = 1

@@

\includegraphics{figure_4.pdf}
**Figure 4. 1-day PEG treatment renders mice susceptible to transient *C. difficile* colonization.** A. Setup of the experimental timeline for the 1-day PEG treated subset of mice. B. CFU/gram stool measured over time (N = 6 mice per timepoint) via several dilutions. The black dotted line represents the limit of detection for the first serial dilution. Asterisks indicate timepoints where the CFU/gram was siginificantly different between groups using the Kruskall-Wallis test with a Benjamini-Hochberg correction for multiple timepoints. C. Principle Coordinate Analysis plot of the groups over time with the alpha representating the same time scale as in panel D (P = `r fig_4_pval` R^2^ = `r fig_4_rsq`). D. Shannon Diveristy Index of the groups over time. Only days with samples from all groups are shown. Samples for some mice were difficult to obtain 
due to the laxative treatment. The alpha scale follows accordingly with the timeline. E. Line plots of relative percent abundance of selected genera over time. Only days with samples from all groups shown. The gray line represents the limit of detection.

>>>>

library(tidyverse)
library(knitr)
library(here)

@@

@@

``` {r figure_4_permnova}
one_day_permnova_results <- read_tsv(here("data/process/1_day_PEG_permanova.tsv"))
one_day_top_2_contrib <- one_day_permnova_results %>% arrange(desc(R2)) %>%
  top_n(3, R2)
one_day_top_contrib_name = (one_day_top_2_contrib[2,1])
one_day_sec_contrib_name = (one_day_top_2_contrib[3,1])
top_R2 = one_day_top_2_contrib[2,6]
sec_R2 = one_day_top_2_contrib[3,6]
```
\includegraphics{figure_4.pdf}
**Figure 4. 1-day PEG treatment renders mice susceptible to transient *C. difficile* colonization.** A. Setup of the experimental timeline for the 1-day PEG treated subset of mice. B. CFU/gram stool measured over time (N = 6 mice per timepoint) via several dilutions. The black dotted line represents the limit of detection for the first serial dilution. Asterisks indicate timepoints where the CFU/gram was siginificantly different between groups using the Kruskall-Wallis test with a Benjamini-Hochberg correction for multiple timepoints. C. Principle Coordinate Analysis plot of the groups over time with the alpha representating the same time scale as in panel D (`r one_day_top_contrib_name`: R^2^ = `r top_R2`; `r one_day_sec_contrib_name`: R^2^ = `r sec_R2`). D. Shannon Diveristy Index of the groups over time. Only days with samples from all groups are shown. Samples for some mice were difficult to obtain 
due to the laxative treatment. The alpha scale follows accordingly with the timeline. E. Line plots of relative percent abundance of selected genera over time. Only days with samples from all groups shown. The gray line represents the limit of detection.

### 2021-04-08 submission/manuscript.tex
Add R-sq values to fig 4 legend and update readme with here package

\includegraphics{figure_4.pdf} \textbf{Figure 4. 1-day PEG treatment
renders mice susceptible to transient \emph{C. difficile} colonization.}
A. Setup of the experimental timeline for the 1-day PEG treated subset
of mice. B. CFU/gram stool measured over time (N = 6 mice per timepoint)
via several dilutions. The black dotted line represents the limit of
detection for the first serial dilution. Asterisks indicate timepoints
where the CFU/gram was siginificantly different between groups using the
Kruskall-Wallis test with a Benjamini-Hochberg correction for multiple
timepoints. C. Principle Coordinate Analysis plot of the groups over
time with the alpha representating the same time scale as in panel D (P
= 1 R\textsuperscript{2} = 1). D. Shannon Diveristy Index of the groups
over time. Only days with samples from all groups are shown. Samples for
some mice were difficult to obtain due to the laxative treatment. The
alpha scale follows accordingly with the timeline. E. Line plots of
relative percent abundance of selected genera over time. Only days with
samples from all groups shown. The gray line represents the limit of
detection.

>>>>

\includegraphics{figure_4.pdf} \textbf{Figure 4. 1-day PEG treatment
renders mice susceptible to transient \emph{C. difficile} colonization.}
A. Setup of the experimental timeline for the 1-day PEG treated subset
of mice. B. CFU/gram stool measured over time (N = 6 mice per timepoint)
via several dilutions. The black dotted line represents the limit of
detection for the first serial dilution. Asterisks indicate timepoints
where the CFU/gram was siginificantly different between groups using the
Kruskall-Wallis test with a Benjamini-Hochberg correction for multiple
timepoints. C. Principle Coordinate Analysis plot of the groups over
time with the alpha representating the same time scale as in panel D
(day: R\textsuperscript{2} = 0.43; group: R\textsuperscript{2} = 0.19).
D. Shannon Diveristy Index of the groups over time. Only days with
samples from all groups are shown. Samples for some mice were difficult
to obtain due to the laxative treatment. The alpha scale follows
accordingly with the timeline. E. Line plots of relative percent
abundance of selected genera over time. Only days with samples from all
groups shown. The gray line represents the limit of detection.
